Aquifer depletion exacerbates agricultural drought losses in the US High Plains

### 2023-11-03 Writing/nw_manuscript.Rnw
update readme

Funding for the research in this manuscript was provided by the United States Department of Agriculture under contract numbers OCE 58-0111-20-007 and OCE 58-0111-21-007 and the Daugherty Water for Food Global Institute at the University of Nebraska. This research was also supported by Innovate UK award no. 10044695, as part of the UK Research and Innovation and European Commission funded project ``TRANSCEND: Transformational and robust adaptation to water scarcity and climate change under deep uncertainty.'' The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

@@

\subsection*{Author Contributions}

\subsection*{Competing Interests Statement}

>>>>

Funding for the research in this manuscript was provided by the United States Department of Agriculture under contract numbers OCE 58-0111-20-007 and OCE 58-0111-21-007 and the Daugherty Water for Food Global Institute at the University of Nebraska. This research was also supported by Innovate UK award no. 10044695, as part of the UK Research and Innovation and European Commission funded project ``TRANSCEND: Transformational and robust adaptation to water scarcity and climate change under deep uncertainty.''

The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

@@

\section*{Author Contributions}

T.M. conceived the paper, developed the computer programs for data collection, processing, analysis, and summarization, and wrote the paper.; T.F. conceived and wrote the paper; S.K. wrote the computer programs for data collection and processing; and N.B. conceived and helped improve the framing of the paper.

\section*{Competing Interests Statement}

The authors declare no competing interests.
